Estimating Daily Bicycle Counts in Seattle from Seasonal and Weather Factors

### 2014-12-25 article/article.tex
final rev for class

A literature review accompanying a recent report by
\textcite{Bassok:2011aa} identified eleven primary indicators, which are
time of day \parencite{Schwartz:1999aa}, season \parencite{Niemeier:1996aa},
population and employment densities
\parencite{McCahil:2008aa,Pinjari:2009aa}, mix of use
\parencite{Pinjari:2009aa}, bicycle facility type \parencite{Hunt:2007aa},
traffic volume \parencite{McDonald:2007aa}, rain and temperature
\parencite{Niemeier:1996aa,Parkin:2008aa},
income \parencite{Turner:1998aa}, and age \parencite{Hunt:2007aa}.
This section outlines the key points made in the literature that are
relevant to some of most important variables.

Research has found the variability for counts has a positive
association with high temperature and low precipitation. \parencite{Niemeier:1996aa,Parkin:2008aa}. Meanwhile, as suggested by
\textcite{Lewin:2011aa} and \textcite{Thomas:2009aa}, the effects of
precipitation and temperature on bicycle volumes are nonlinear. For
example, bicycle traffic can decrease in both very cold and very hot
weather as noted by \textcite{Richardson:2000aa}. Apart from the usual
temperature and rain variables, \textcite{Miranda-Moreno:2011aa} finds
humidity and additional precipitation variables including the presence
of rain in the morning and/or during the previous three hours to be
significant too. Other comparative studies are also available where
bicycle counts are conducted in different cities and different
sensitives to weather are examined \parencite{Rose:2011aa}. As for
longitudinal studies, \textcite{Niemeier:1996aa} finds increased variability
for counts conducted in the later months of the year.
\textcite{Jones:2010aa} conclude that morning peak hours from 6 AM to 9 PM
accounts for a consistent 95\% of the total bicycle volumes by hourly
count data. The simple linear regression model has been used in
several applications \cite{Jones:2008aa,Jones:2010aa}. Other modeling approaches include \cite{Miranda-Moreno:2011aa} which develops a count
model and \cite{Thomas:2009aa} which develops a time-series model.
\cite{Niemeier:1996aa} also uses a Poisson model to statistically
confirm  many of the factors thought to influence cyclists. The
work by \cite{Gallop:2012aa} adopts a similar time-series approach
while incorporating an autoregressive integrated moving average
(ARIMA) analysis. A summary of findings from the literature are
presented in table \ref{tb:lit}.

@@

\newfixedcaption{\freetabcaption}{table}
\begin{centering}
\begin{scriptsize}
\freetabcaption{Summary of findings from literature review}
\begin{ctabular}{p{.6in}p{1.15in}p{1.15in}}
  \toprule
  Source & Variable(s) identified & Methods \\
  \midrule
  \cite{Fields:2012aa} & Average daily temperature (F); Total weekly precipitation (inches) & Identify patterns through scatter plots; No explicit model is established. \\
  \cite{Gallop:2012aa} & Temperature, Relative humidity, wind speed, clearness,fog, precipitation & Use ARIMA to account for serial correlation patterns \\
  \cite{Griswold:2011aa} & Nearby population and employment density, proximity to downtown/freeway, age, education level, income, et. & Log linear ordinary least squares regression is used to estimate a bicycle count model \\
  \cite{Helbich:2014aa} & Daily maiximum air temperature (C), daily average wind speed (m/s), daily precipitation(mm) & Place-specific associations of weather conditions are explored through geographically weighted logit models \\
  \cite{Hunt:2007aa} & Descriptive variables indicating lane use, secured parking, level of experience, etc. & Logistic model of cycling-related choices \\
  \cite{Jones:2010aa} & Length of bicycle network, employment density, population density & Standard ordinary least squares regression \\
  \cite{Lewin:2011aa} & Max temp (F), rain flag, snow flag, weekend flag, over 90 flag & Standard linear regression model \\
  \cite{McCahil:2008aa} & logarithmic choice measure, population density, worker density & A new space syntax theory is used to evaluate and predict the bicycle volume throughout a network \\
  \cite{Miranda-Moreno:2011aa} & Temperature (C), humidity (\%), rain presence (0/1), rain in prev. 3hrs (0/1), warm \& humid (0/1), morning rain (0/1) & Both log-linear model and negative binomial model are tested \\
  \cite{Niemeier:1996aa} & Morning flag, rain flag, high temp flag, location variable, season variable & A Poisson bicycle count model is assumed and fitted \\
  \cite{Nosal:2014aa} & Temperature (F), humidity (\%), rain flag, rain prev. 3hrs, am rain, pm rain & The relationship  is analyzed using a log-linear regression model \\
  \cite{Parkin:2008aa} & Gender, car ownership, hilliness, off-road routes proportion & A logistic regression model of relevant socio-economic and physical variables is estimated. \\
  \cite{Pinjari:2009aa} & Household density, employment density, fraction of commercial land area, fraction of senior, fraction of race population, etc. & The model system takes the form of a joint mixed Multinomial Logit–Multiple Discrete-Continuous Extreme Value (MNL–MDCEV) structure \\
  \cite{Rose:2011aa} & Temerature(C), rainfall(mm), holiday flag, school seanson flag, day of the week & Weather and other effects examined using an aggregate model of daily ridership \\
  \cite{Thomas:2009aa} & Temperature(C), sunshine(h), precipitation(mm), wind force(m/s), cycle path use & A bi-level structure is developed with the upper level being a log-linear model and the lower level being a linear model \\
  \bottomrule
\label{tb:lit}
\end{ctabular}
\end{scriptsize}
\end{centering}

@@

\subsection*{Data collection, processing, description}
%
% Data collection: study site, descriptives of sample, collection from
% forecast.io and seattle.gov, not in that order
%

The data that we attempt to explain were collected at Seattle's
Fremont Bridge and cover a period of two years spanning from October
31, 2012 to October 30, 2014. The Fremont Bridge captures a
substantial number of bicyclists due to its status as one of only five
facilities that carry bicyclists across the canal that separates the
northern and southern halves of Seattle. Bicycle counts are collected
at this location continuously by the City of Seattle using an
in-sidewalk counter manufactured by EcoCounter. When a bicycle passes
over an induction loop embedded in the sidewalk on either side of the
Fremont Bridge, the counter registers the bicycle. Bicyclists may
legally choose to ride in the roadway instead of the sidewalk, and
would not be detected by the counter. However, we believe these
crossings are rare at this location due to the design of the facility,
which directs bicyclists to enter the sidewalk, and from our own
experience riding and observing other riders. Counts are aggregated
into 15 minute intervals, and are made available to the public via the
City of Seattle's data
portal \parencite{City-of-Seattle:aa,City-of-Seattle:ab}.

Weather data are aggregated and made available through Forecast.io's
web services API \parencite{The-Dark-Sky-Company:aa}. Historical daily
summaries are available for a range of weather variables including
several specifically important to our model such as precipitation,
daily minimum and maximum temperatures, sunrise, and sunset.

We downloaded and processed these data programmatically using the R
programming language along with several add-on
packages \parencite{Grolemund:2011aa,Wickham:2011aa,Couture-Beil:2014aa,Lang:2014aa,R-Core-Team:2014aa}.
Bicycle counts were aggregated by day, and then joined to weather data
by date. In addition to the variables collected from these two
sources, we were also interested in controlling for holidays and
whether or not the nearby University of Washington was in session.
These data were collected and coded manually from the University of
Washington's historic academic calendars.

Figures \ref{fg:hist} and \ref{fg:timeseries} provide visual summaries
of the processed counts data.

@@

\subsection*{Variable selection}
% 
% Data analysis: specification of model, choice of model (nb v pois),
% description of counterfactual simulation using the estimated model,
% software used.
%

@@

\begin{centering}
\begin{table}[ht!]
\begin{scriptsize}
\caption{Variables included in model specification}
\begin{tabularx}{0.47\textwidth}{>{\raggedright\arraybackslash}p{1.6cm}>{\raggedright\arraybackslash}X}
\toprule
Variable & Description \\
\midrule
Count* & Number of bicycles per day \\
Daylight  & Length of daylight in hours \\
UW & The University of Washington in session (TRUE/FALSE) \\
Holiday & The day a holiday as recognized by UW (TRUE/FALSE) \\
Max temp & Maximum temperature in Fahrenheit for the day \\
Max precip & Daily maximum inches of precipitation in any hour \\
Sat--Fri & Day of the week dummy variable (TRUE/FALSE, relative to Sunday) \\
Day \# & Sequentially numbered day of study \\
\bottomrule
\multicolumn{2}{r}{* Dependent variable}
\end{tabularx}

@@

Daylight hours (defined as $sunset - sunrise$) and the University of
Washington in-session status were selected to represent seasonality.
Daylight hours was chosen instead of a calendar-based categorization
of season in part because Seattle's Pacific Maritime Climate differs
substantially from traditional notions of Spring, Summer, Autumn, and
Winter. Daylight hours also is measured as a continuous value at a
finer temporal resolution of one day. Finally, daylight hours adjusts
according to latitude, which may make this model estimation procedure
and specification more transferable to other sites in the future.

We deemed the University of Washington variable important in part
because of the Fremont Bridge's proximity and connection via the Burke
Gilman Trail to the University of Washington. We also felt that this
variable was a suitable proxy for the ``school season,'' which more
broadly captures whether or not local schools are in session. The
academic calendars of the various local schools do not align
perfectly, however they still overlap substantially with the
University of Washington, which is itself the largest educational
institution in the region.

@@

\subsection*{Model estimation and goodness of fit}
% Model choice
A natural model choice for count data is the Poisson model, however we
believed that our count data were overdispersed. Overdispersion, or
contagion between events, violates the mean-variance equivalence
assumption of the Poisson model. While overdispersion would not impact
our parameter estimates, it would result in overly optimistic margins
of error. In order to account for and estimate the amount of
overdispersion present in our data, we chose a negative binomial model
type. Because there were no days observed with zero bicycle counts, we
did not need to resort to zero-inflated models as is often necessary
when dealing with count data.

% Estimation method
We fit the model in R using the \texttt{glm.nb} function from the MASS
package \parencite{Venables:2002aa}. For comparison, we also estimated a
Poisson model with an analogous specification in R using the
\texttt{glm} function. A much lower AIC and BIC in the case of the
negative binomial model confirmed that it was a better fit than the
Poisson. We then tested for overdispersion using the \texttt{odTest} function
from the Pscl package \parencite{Jackman:2014aa}. The highly significant
chi-square test statistic provided strong evidence that overdispersion
was present in the data, further confirming the choice of a negative
binomial.

In addition to testing the model fit relative to its Poisson
analog, we visually assessed the fit of our negative binomial model by
plotting actual versus predicted values as shown in figure
\ref{fg:avp}. This fit appears to be generally good, though very high
count days are predicted somewhat less accurately.

@@

% Model interpretation
In order to provide results that are more readily interpretable by
non-statisticians, we used counterfactual simulation to isolate
individual terms from the model that correspond to our research
questions. In so doing, we generated various quantities of interest
including point estimates and confidence intervals, and then plotted
them for visual inspection. Counterfactual simulations were performed
with a modified version of the Simcf R package, and visualized with
ggplot2 \parencite{Adolph:2014aa,Schmiedeskamp:aa,Wickham:2009aa}.
Results of these simulations are presented in the following section.

@@

Without exception, each of the coefficients in our model was
statistically significant at the $p < 0.05$. Further, with the
exception of the Saturday coefficient, all coefficients were
significant at the $p < 0.001$ level. The remainder of this section
focuses on presenting the substantive effect of each variable.

\subsection*{Seasonality}
As discussed previously, we considered two variables to address the
question of seasonality: the first being the number of daylight hours,
and the second being whether or not the University of Washington
(proxying more generally for other educational institutions) was in
session.

Figure \ref{fg:seasonality} shows that we see a substantial increase
in bicycle volumes when the University of Washington is in session.
With all other factors held constant we see that, on days when the
university is in session, there is an average of approximately 367
additional bicycles observed. Similarly, we see a roughly linear
increase in bicycles with increased day length.

>>>>

A literature review accompanying a recent report by
\textcite{Bassok:2011aa} identified eleven primary indicators. These included 
time of day \parencite{Schwartz:1999aa}, season \parencite{Niemeier:1996aa},
population and employment densities
\parencite{McCahil:2008aa,Pinjari:2009aa}, land-use mix
\parencite{Pinjari:2009aa}, bicycle facility type \parencite{Hunt:2007aa},
traffic volume \parencite{McDonald:2007aa}, rain and temperature
\parencite{Niemeier:1996aa,Parkin:2008aa},
income \parencite{Turner:1998aa}, and age \parencite{Hunt:2007aa}.
This section outlines the key points made in the literature that are
relevant to some of most important variables.

Research has found the variability for counts has a positive
association with high temperature and low precipitation. \parencite{Niemeier:1996aa,Parkin:2008aa}. Meanwhile, as suggested by
\textcite{Lewin:2011aa} and \textcite{Thomas:2009aa}, the effects of
precipitation and temperature on bicycle volumes are nonlinear. For
example, bicycle traffic can decrease in both very cold and very hot
weather as noted by \textcite{Richardson:2000aa}. Apart from the usual
temperature and rain variables, \textcite{Miranda-Moreno:2011aa} finds
humidity and additional precipitation variables including the presence
of rain in the morning and/or during the previous three hours to be
significant too. Other comparative studies are also available where
bicycle counts are conducted in different cities, and different
sensitives to weather are examined \parencite{Rose:2011aa}. As for
longitudinal studies, \textcite{Niemeier:1996aa} finds increased variability
for counts conducted in the later months of the year.
\textcite{Jones:2010aa} conclude that morning peak hours from 6 AM to 9 PM
accounts for a consistent 95\% of the total bicycle volumes by hourly
count data. The simple linear regression model has been used in
several applications \parencite{Jones:2008aa,Jones:2010aa}. Other modeling approaches include \textcite{Miranda-Moreno:2011aa} which develops a count
model and \textcite{Thomas:2009aa} which develops a time-series model.
\textcite{Niemeier:1996aa} also uses a Poisson model to statistically
confirm  many of the factors thought to influence cyclists. The
work by \textcite{Gallop:2012aa} adopts a similar time-series approach
while incorporating an autoregressive integrated moving average
(ARIMA) analysis. A summary of findings from the literature are
presented in table \ref{tb:lit}.

@@

\newfixedcaption{\freetabcaption}{table}
\begin{centering}
\begin{scriptsize}
\freetabcaption{Summary of findings from literature review}
\begin{ctabular}{p{.6in}p{1.15in}p{1.15in}}
  \toprule
  Source & Variable(s) identified & Methods \\
  \midrule
  \cite{Fields:2012aa} & Average daily temperature (F); Total weekly precipitation (inches) & Identify patterns through scatter plots; No explicit model is established. \\
  \cite{Gallop:2012aa} & Temperature, Relative humidity, wind speed, clearness,fog, precipitation & Use ARIMA to account for serial correlation patterns \\
  \cite{Griswold:2011aa} & Nearby population and employment density, proximity to downtown/freeway, age, education level, income, et. & Log linear ordinary least squares regression is used to estimate a bicycle count model \\
  \cite{Helbich:2014aa} & Daily maiximum air temperature (C), daily average wind speed (m/s), daily precipitation(mm) & Place-specific associations of weather conditions are explored through geographically weighted logit models \\
  \cite{Hunt:2007aa} & Descriptive variables indicating lane use, secured parking, level of experience, etc. & Logistic model of cycling-related choices \\
  \cite{Jones:2010aa} & Length of bicycle network, employment density, population density & Standard ordinary least squares regression \\
  \cite{Lewin:2011aa} & Max temp (F), rain flag, snow flag, weekend flag, over 90 flag & Standard linear regression model \\
  \cite{McCahil:2008aa} & logarithmic choice measure, population density, worker density & A new space syntax theory is used to evaluate and predict the bicycle volume throughout a network \\
  \cite{Miranda-Moreno:2011aa} & Temperature (C), humidity (\%), rain presence (0/1), rain in prev. 3hrs (0/1), warm \& humid (0/1), morning rain (0/1) & Both log-linear model and negative binomial model are tested \\
  \cite{Niemeier:1996aa} & Morning flag, rain flag, high temp flag, location variable, season variable & A Poisson bicycle count model is assumed and fitted \\
  \cite{Nosal:2014aa} & Temperature (F), humidity (\%), rain flag, rain prev. 3hrs, am rain, pm rain & The relationship  is analyzed using a log-linear regression model \\
  \cite{Parkin:2008aa} & Gender, car ownership, hilliness, off-road routes proportion & A logistic regression model of relevant socio-economic and physical variables is estimated. \\
  \cite{Pinjari:2009aa} & Household density, employment density, fraction of commercial land area, fraction of senior, fraction of race population, etc. & The model system takes the form of a joint mixed Multinomial Logit–Multiple Discrete-Continuous Extreme Value (MNL-MDCEV) structure \\
  \cite{Rose:2011aa} & Temerature(C), rainfall(mm), holiday flag, school seanson flag, day of the week & Weather and other effects examined using an aggregate model of daily ridership \\
  \cite{Thomas:2009aa} & Temperature(C), sunshine(h), precipitation(mm), wind force(m/s), cycle path use & A bi-level structure is developed with the upper level being a log-linear model and the lower level being a linear model \\
  \bottomrule
\label{tb:lit}
\end{ctabular}
\end{scriptsize}
\end{centering}

@@

\FloatBarrier
\subsection*{Data collection, processing, description}
%
% Data collection: study site, descriptives of sample, collection from
% forecast.io and seattle.gov, not in that order
%

The data that we attempt to explain were collected at Seattle's
Fremont Bridge and cover a period of two years spanning from October
31, 2012 to October 30, 2014. The Fremont Bridge captures a
substantial amount of bicycle traffic due to its status as one of only
five facilities that carry bicyclists across the canal separating the
northern and southern halves of Seattle.

Bicycle counts were collected at this location continuously by the
City of Seattle using an in-sidewalk counter manufactured by
EcoCounter. When a bicycle passes over an induction loop embedded in
the sidewalk on either side of the Fremont Bridge, the counter
registers the bicycle. Bicyclists may legally choose to ride in the
roadway instead of the sidewalk, and would thus not be detected by the
counter. However, we believe these crossings are rare at this location
due to the design of the facility, which directs bicyclists to enter
the sidewalk, and from our own experience riding and observing other
riders. Counts are aggregated into 15 minute intervals by the City of
Seattle, and are made available to the public via the City of
Seattle's data
portal \parencite{City-of-Seattle:aa,City-of-Seattle:ab}.

Weather data are collected by a variety of sources and are aggregated
by Forecast.io. These data are available through the company's web
services API \parencite{The-Dark-Sky-Company:aa}. Historical daily
summaries are available for a range of weather variables including
several specifically important to our model such as precipitation,
daily minimum and maximum temperatures, sunrise, and sunset.

We downloaded and processed these data programmatically using the R
programming language along with several add-on
packages \parencite{Grolemund:2011aa,Wickham:2011aa,Couture-Beil:2014aa,Lang:2014aa,R-Core-Team:2014aa}.\footnote{In
addition, the code used to run the analysis, as well as the final
dataset are available as a github repository: \url{https://github.com/pschmied/bikecounts-mle}}
Bicycle counts were aggregated by day, and then joined to weather data
by date. In addition to the variables collected from these two
sources, we were also interested in controlling for holidays and
whether or not the nearby University of Washington was in session.
These data were collected and coded manually from the University of
Washington's historic academic calendars.

Figures \ref{fg:hist} and \ref{fg:timeseries} provide visual summaries
of the processed counts data. Some apparent outliers are visible at
the rightmost portion of the histogram. The two highest counts
occurred the Monday and Tuesday preceding the beginning of National
Bike to Work Month. And the third highest count occurred on National
Bike to Work Day.

@@

\FloatBarrier
\subsection*{Variable selection}
% 
% Data analysis: specification of model, choice of model (nb v pois),
% description of counterfactual simulation using the estimated model,
% software used.
%

@@

\begin{centering}
\begin{table}[ht!]
\begin{scriptsize}
\caption{Variables included in model specification}
\begin{tabularx}{0.47\textwidth}{>{\raggedright\arraybackslash}p{1.6cm}>{\raggedright\arraybackslash}X}
\toprule
Variable & Description \\
\midrule
Count* & Number of bicycles per day \\
Daylight  & Length of daylight in hours \\
UW & The University of Washington was in session (TRUE/FALSE) \\
Holiday & The day was a holiday as recognized by UW (TRUE/FALSE) \\
Max temp & Maximum temperature in Fahrenheit for the day \\
Max precip & Daily maximum inches of precipitation in any hour \\
Sat--Fri & Day of the week dummy variable (TRUE/FALSE, relative to Sunday) \\
Day \# & Sequentially numbered day of study \\
\bottomrule
\multicolumn{2}{r}{* Dependent variable}
\end{tabularx}

@@

Daylight hours (defined as $sunset - sunrise$) and the University of
Washington in-session status were selected to represent seasonality.
Daylight hours was chosen instead of a calendar-based categorization
of season in part because Seattle's Pacific Maritime Climate differs
substantially from traditional notions of Spring, Summer, Autumn, and
Winter. Daylight hours also is measured as a continuous value at a
finer temporal resolution of one day. Finally, daylight hours adjusts
according to latitude, which may make this model estimation procedure
and specification more transferable to other sites in the future,
perhaps by interacting latitude with daylight hours.

We deemed the University of Washington variable important in part
because of the Fremont Bridge's proximity and connection via the Burke
Gilman Trail to the University of Washington. We also felt that this
variable was a suitable proxy for the ``school season,'' which more
broadly captures whether or not other local schools are in session.
The academic calendars of the various local schools do not align
perfectly, however they still overlap substantially with the
University of Washington, which is itself the largest educational
institution in the region.

@@

\FloatBarrier
\subsection*{Model estimation and goodness of fit}
% Model choice
A natural model choice for count data is the Poisson model, however we
believed that our count data were overdispersed. Overdispersion, or
contagion between events, violates the mean-variance equivalence
assumption of the Poisson model. While overdispersion would not impact
our parameter estimates, it would result in overly optimistic margins
of error. In order to account for and estimate the amount of
overdispersion present in our data, we chose a negative binomial model
type. Because there were no days observed with zero bicycle counts, we
did not need to resort to zero-inflated models as is often necessary
when dealing with count data.

% Estimation method
We fit the model in R using the \texttt{glm.nb} function from the MASS
package \parencite{Venables:2002aa}. For comparison, we also estimated
a Poisson model with an analogous specification in R using the
\texttt{glm} function. A much lower AIC and BIC in the case of the
negative binomial model confirmed that it was a better fit than the
Poisson. We then tested for overdispersion using the \texttt{odTest}
function from the Pscl package \parencite{Jackman:2014aa}. The highly
significant chi-squared test statistic provided strong evidence that
overdispersion was present in the data.

Additionally, we compared the residuals plots for both the Poisson and
negative binomial models. As seen in figures \ref{fg:resnb} and
\ref{fg:respois}, the residual variance is much lower in the negative
binomial model, further confirming the choice of a negative
binomial for these counts.

As a final model comparison, we visually assessed the overall fit of
our negative binomial model by plotting actual versus predicted values
as shown in figure \ref{fg:avp}. This fit appears to be generally
good, though very high count days are predicted somewhat less
accurately.

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.5\textwidth]{../fig/residuals_pois}
  \caption{Residual variance from the Poisson model}
  \label{fg:respois}
\end{figure}

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.5\textwidth]{../fig/residuals}
  \caption{Residual variance from the negative binomial model}
  \label{fg:resnb}
\end{figure}

@@

% Model interpretation
In order to provide results that are more readily interpretable by
non-statisticians, we used counterfactual simulation to isolate
individual terms from the model that correspond to our research
questions. In so doing, we simulated various quantities of interest
including point estimates and confidence intervals, and then plotted
them for visual inspection. Counterfactual simulations were performed
with a modified version of the Simcf R package, and visualized with
ggplot2 \parencite{Adolph:2014aa,Schmiedeskamp:aa,Wickham:2009aa}.
Results of these simulations are presented in the following section.

@@

Without exception, each of the coefficients in our model was
statistically significant at the $p < 0.05$ level. Further, with the
exception of the Saturday coefficient, all coefficients were
significant at the $p < 0.001$ level. The remainder of this section
focuses on presenting the substantive effect of each variable.

\FloatBarrier
\subsection*{Seasonality}
As discussed previously, we considered two variables to address the
question of seasonality: the first being the number of daylight hours,
and the second being whether or not the University of Washington
(proxying more generally for other educational institutions) was in
session.

Figure \ref{fg:seasonality} shows that we see a substantial increase
in bicycle volumes when the University of Washington was in session.
With all other factors held constant we see that, on days when the
university is in session, we would expect an average of approximately
367 additional bicycles observed. Similarly, we see a roughly linear
increase in bicycles with increased day length.
